\bf Faster Beam Search for Neural Machine Translation

### 2018-01-10 fast-beam/fast-beam.tex
fast-beam

In addition, models with large number of classes frequently desire a list of the n-best classes rather than just the argmax, further complicating problem.

However, there are algorithmic similarites between each step.

>>>>

In addition, we are interested not just in the argmax value but of beam search for the n-best classes and their probabilities, further complicating the problem.

We shall leave the matrix multiplication for the next proposal and future work, and concentrate on the last three steps. There are algorithmic similarites between these steps, which we outline in ???.

??? alogirthm of each step
